Acid-induced protein gels: from gelation to stress-induced failure

### 2015-10-16 talk_Montpellier.tex
append Soundbite palavas allow pgfplottable relax tables after use

\usepackage{pgfplots}
\pgfplotsset{compat=1.9}
\usepgfplotslibrary{groupplots}
\usepgfplotslibrary{external}
\makeatletter
\newcommand*{\overlaynumber}{\number\beamer@slideinframe}
\tikzset{
  beamer externalizing/.style={%
    execute at end picture={%
      \tikzifexternalizing{%
        \ifbeamer@anotherslide
        \pgfexternalstorecommand{\string\global\string\beamer@anotherslidetrue}%
        \fi
      }{}%
    }%
  },
  external/optimize=false
}
\let\orig@tikzsetnextfilename=\tikzsetnextfilename
\renewcommand\tikzsetnextfilename[1]{\orig@tikzsetnextfilename{#1-\overlaynumber}}
\makeatother

@@

>>>>

\usepackage{pgfplots}
\usepackage{pgfplotstable}
\pgfplotsset{compat=1.9}
\usepgfplotslibrary{groupplots}
\usepgfplotslibrary{external}
\makeatletter
\newcommand*{\overlaynumber}{\number\beamer@slideinframe}
\tikzset{
  beamer externalizing/.style={%
    execute at end picture={%
      \tikzifexternalizing{%
        \ifbeamer@anotherslide
        \pgfexternalstorecommand{\string\global\string\beamer@anotherslidetrue}%
        \fi
      }{}%
    }%
  },
  external/optimize=false
}
\let\orig@tikzsetnextfilename=\tikzsetnextfilename
\renewcommand\tikzsetnextfilename[1]{\orig@tikzsetnextfilename{#1-\overlaynumber}}
\makeatother

@@

\begin{frame}{Over-acidified protein gels: beyond isoelectric pH}
	\tikzsetnextfilename{prise_cas4}
	\input{fig_soundbite_palavas/prise_cas4.pgf}
	\begin{itemize}
	\item[$\Rightarrow$] still solid
	\end{itemize}
\end{frame}

\begin{frame}{Linear rheology, from power-law to soft glassy}
	\tikzsetnextfilename{sweep_cas4}
	\input{fig_soundbite_palavas/sweep_cas4.pgf}
	\begin{itemize}
	\item Near isoelectric, power law rheology $G^\prime, G^{\prime\prime}$ typical of gels 
	\item Over-acidification lowers exponent and creates a minimum in $G^{\prime\prime}$
	\item Transition to soft-glassy behaviour \\\textit{\footnotesize Sollich, PRE (1998); Mason, Curr. Opin. Colloid Interface Sci. (1999)}
	\end{itemize}
\end{frame}

\begin{frame}{Questions}
\begin{description}
\item[What] is the change in microstructure?
\item[How] does it affects the failure mechanism?
\end{description}
\end{frame}

\begin{frame}{Microscructure: fluorescent confocal microscopy}
	\tikzsetnextfilename{structure_confocal}
	\input{fig_soundbite_palavas/structure_confocal.pgf}
	\begin{itemize}
	\item Maximum $G^\prime$ corresponds to maximum contrast between phases
	\item Characteristic size $\xi$ increases during over-acidification
	\item Casein aggregates swell $\sim$ over compressed gel $\Rightarrow$ soft glassy
	\end{itemize}
\end{frame}

\begin{frame}{Three creep regimes + softness\hfill\textsc{gdl} 4\%}
\vfill
	\tikzsetnextfilename{creep_cas4_gdl4}
	\input{fig_soundbite_palavas/creep_cas4_gdl4.pgf}
\begin{itemize}
%\item Failure scenario almost conserved: ``fibre bundle'' network
%\item Other dissipation due to softness: overcompressed gel
\item More difficult to predict failure time from fractures nucleation time
\end{itemize}

\end{frame}
